---
title: "BTC"
author: "Simon Steyskal"
date: "24 Juni 2016"
output: html_document
---

<style>
  .col2 {
    columns: 2 200px;         /* number of columns and width in pixels*/
    -webkit-columns: 2 200px; /* chrome, safari */
    -moz-columns: 2 200px;    /* firefox */
    min-height: 360px;
  }
  .col3 {
    columns: 3 100px;
    -webkit-columns: 3 100px;
    -moz-columns: 3 100px;
  	min-height: 200px;
  }
.main-container {
  max-width: 2048px;
}
</style>



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages, include=FALSE}
library(plotly)
```

## Calculating Number of BTC Transaction Inputs/outputs

```{r, eval=F}
Bash: awk -F, '{a[$1]++;}END{for (i in a)print i, a[i];}' tx_input_address.csv > nrInputsPerTX.csv
Bash: awk -F, '{a[$1]++;}END{for (i in a)print i, a[i];}' tx_output_address.csv > nrOutputsPerTX.csv
```

### Loading both csv in R

```{r, eval=FALSE}
nrInputsPerTX <- read.csv("nrInputsPerTX.csv", stringsAsFactors=FALSE)
nrOutputsPerTX <- read.csv("nrOutputsPerTX.csv", stringsAsFactors=FALSE)
```
*** 
```{r, echo=FALSE}
nrInputsPerTX <- read.csv("C:/Users/ssteyska/Desktop/sorted_nrInputsPerTX.csv", stringsAsFactors=FALSE)
nrOutputsPerTX <- read.csv("C:/Users/ssteyska/Desktop/sorted_nrOutputsPerTX.csv", stringsAsFactors=FALSE)
```

### Characteristics

#### Distinct Input Addresses per Transaction
<div class="col3">
```{r}
head(nrInputsPerTX)
tail(nrInputsPerTX)
summary(nrInputsPerTX$amount)
```
</div>
*** 
#### Distinct Output Addresses per Transaction
<div class="col3">
```{r}
head(nrOutputsPerTX)
tail(nrOutputsPerTX)
summary(nrOutputsPerTX$amount)
```
</div>
*** 
### Calculating Percentage of Transactions having 1..100 Inputs/Outputs
```{r}
inputsPerTx = NULL
amount <- nrInputsPerTX$amount
for(i in 1:100) {
 inputsPerTx = rbind(inputsPerTx, data.frame(nrIn=i,am=100 * length(which(amount == i)) / length(amount)))
}
```

```{r}
outputsPerTx = NULL
amount2 <- nrOutputsPerTX$amount
for(i in 1:100) {
 outputsPerTx = rbind(outputsPerTx, data.frame(nrIn=i,am=100 * length(which(amount2 == i)) / length(amount2)))
}
```

### Results
#### Inputs
<div class="col2">
* Out of 2923321 transactions [^1]:
    + 79% have only one input
    + 10% have 2 inputs
    + 99.55% have <= 10 inputs
```{r}
head(inputsPerTx)
plot_ly(inputsPerTx,labels=nrIn,values=am, type="pie",showlegend = F)%>%
  layout(width = 300, height = 300)
```
</div>
*** 
#### Outputs
<div class="col2">
* Out of 3103109 transactions:
    + 25.57% have only one output
    + 73% have 2 outputs
    + 99.1% have <= 5 outputs
```{r}
head(outputsPerTx)
plot_ly(outputsPerTx,labels=nrIn,values=am, type="pie",showlegend = F)%>%
  layout(width = 300, height = 300)
```
</div>


[^1]: 179788 transactions had no input